Investigating factors that may influence COVID-19 survival

### 2022-01-09 manuscript.Rmd
Update manuscript.Rmd

---
title: Template for Oxford University Press papers
author:
  - name: Alpha Beta
    email: alpha@university.ac.uk
    corresponding_author: TRUE # Automatic footnote using corresponding_author
    affiliation:
      - ABC
      - DEF
    biography: |
      A researcher.
      #    biography_pic: "/PATH/TO/image.png"
      #    biography_pic_width: "1in"
  - name: Beta Gamma
    email: beta@university.ac.uk
    affiliation: DEF
    footnote: 1 # Footnote using reference
  - name: Zeta Epsilon
    email: zeta@institution.ac.uk
    affiliation: XYZ
    footnote:
        - 1
        - 2
address:
  - code: ABC
    department: Department of Biology
    organization: University
  - code: DEF
    address: University
  - code: XYZ
    address: Institution
footnote:
  - code: 1
    text: "Equal contribution"
  - code: 2
    text: "Current email address: [alpha@university.ac.uk](mailto:alpha@university.ac.uk)"
abstract:
  - "**Objective:**  To Investigate, and identify, the factors that may influence patient survival of coronavirus disease 19."
  - "More"
  - "**Motivation:** You can also have some paragraphs start with bold face."
keywords:
  - mathematics
  - survival
  - prognostics
competing_interests: |
  There are no competing interest.
author_contributions: |
  Equal contributions
acknowledgements: |
  This is an acknowledgement.

  It consists of two paragraphs.

>>>>

---
title: Investigating factors that may influence COVID-19 survival
author:
  - name: 36112895
    email: 36112895@lancaster.ac.uk
    corresponding_author: TRUE
    affiliation:
      - A
    footnote:
      - 1
address:
  - code: A
    department: Lancaster Medical School
    organization: University of Lancaster
footnote:
  - code: 1
    text: "Postgraduate Student"
abstract:
  - "**Objective:**  To Investigate, and identify, the factors that may influence patient survival of coronavirus disease 19."
  - "More"
  - "**Motivation:** You can also have some paragraphs start with bold face."
keywords:
  - mathematics
  - survival
  - prognostics
